XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-24 talk/icooolps2011/code/interpreter-slow.tex
more figureyfication

\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{class} \PY{n+nc}{Map}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{indexes} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{other\PYZus{}maps} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

    \PY{n+nd}{@purefunction}
    \PY{k}{def} \PY{n+nf}{getindex}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{indexes}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{,} \PY{o}{-}\PY{l+m+mi}{1}\PY{p}{)}

    \PY{n+nd}{@purefunction}
    \PY{k}{def} \PY{n+nf}{add\PYZus{}attribute}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{k}{if} \PY{n}{name} \PY{o+ow}{not} \PY{o+ow}{in} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{other\PYZus{}maps}\PY{p}{:}
            \PY{n}{newmap} \PY{o}{=} \PY{n}{Map}\PY{p}{(}\PY{p}{)}
            \PY{n}{newmap}\PY{o}{.}\PY{n}{indexes}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{indexes}\PY{p}{)}
            \PY{n}{newmap}\PY{o}{.}\PY{n}{indexes}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n+nb}{len}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{indexes}\PY{p}{)}
            \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{other\PYZus{}maps}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{newmap}
        \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{other\PYZus{}maps}\PY{p}{[}\PY{n}{name}\PY{p}{]}

\PY{n}{EMPTY\PYZus{}MAP} \PY{o}{=} \PY{n}{Map}\PY{p}{(}\PY{p}{)}

\PY{k}{class} \PY{n+nc}{Instance}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{cls}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{cls} \PY{o}{=} \PY{n}{cls}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{map} \PY{o}{=} \PY{n}{EMPTY\PYZus{}MAP}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{storage} \PY{o}{=} \PY{p}{[}\PY{p}{]}

    \PY{k}{def} \PY{n+nf}{getfield}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n+nb}{map} \PY{o}{=} \PY{n}{hint}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{map}\PY{p}{,} \PY{n}{promote}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
        \PY{n}{index} \PY{o}{=} \PY{n+nb}{map}\PY{o}{.}\PY{n}{getindex}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{index} \PY{o}{!=} \PY{o}{-}\PY{l+m+mi}{1}\PY{p}{:}
            \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{storage}\PY{p}{[}\PY{n}{index}\PY{p}{]}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{write\PYZus{}attribute}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb}{map} \PY{o}{=} \PY{n}{hint}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{map}\PY{p}{,} \PY{n}{promote}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
        \PY{n}{index} \PY{o}{=} \PY{n+nb}{map}\PY{o}{.}\PY{n}{getindex}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{index} \PY{o}{!=} \PY{o}{-}\PY{l+m+mi}{1}\PY{p}{:}
            \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{storage}\PY{p}{[}\PY{n}{index}\PY{p}{]} \PY{o}{=} \PY{n}{value}
            \PY{k}{return}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{map} \PY{o}{=} \PY{n+nb}{map}\PY{o}{.}\PY{n}{add\PYZus{}attribute}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{storage}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{value}\PY{p}{)}

>>>>

\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{class} \PY{n+nc}{Class}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{n}{name}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

    \PY{k}{def} \PY{n+nf}{instantiate}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{)}\PY{p}{:}
        \PY{k}{return} \PY{n}{Instance}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{find\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n}{result} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{result} \PY{o+ow}{is} \PY{o+ow}{not} \PY{n+nb+bp}{None}\PY{p}{:}
            \PY{k}{return} \PY{n}{result}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{change\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{value}

\PY{k}{class} \PY{n+nc}{Instance}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{cls}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{cls} \PY{o}{=} \PY{n}{cls}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

    \PY{k}{def} \PY{n+nf}{getfield}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n}{result} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{result} \PY{o+ow}{is} \PY{o+ow}{not} \PY{n+nb+bp}{None}\PY{p}{:}
            \PY{k}{return} \PY{n}{result}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{write\PYZus{}attribute}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{value}

### 2011-03-24 talk/icooolps2011/code/version.tex
more figureyfication

\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{class} \PY{n+nc}{Class}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{n}{name}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

    \PY{k}{def} \PY{n+nf}{instantiate}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{)}\PY{p}{:}
        \PY{k}{return} \PY{n}{Instance}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{find\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n}{result} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{result} \PY{o+ow}{is} \PY{o+ow}{not} \PY{n+nb+bp}{None}\PY{p}{:}
            \PY{k}{return} \PY{n}{result}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{change\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{value}

\PY{k}{class} \PY{n+nc}{Instance}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{cls}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{cls} \PY{o}{=} \PY{n}{cls}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

    \PY{k}{def} \PY{n+nf}{getfield}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n}{result} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{if} \PY{n}{result} \PY{o+ow}{is} \PY{o+ow}{not} \PY{n+nb+bp}{None}\PY{p}{:}
            \PY{k}{return} \PY{n}{result}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{write\PYZus{}attribute}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{attributes}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{value}

    \PY{k}{def} \PY{n+nf}{getattr}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{k}{try}\PY{p}{:}
            \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{getfield}\PY{p}{(}\PY{n}{name}\PY{p}{)}
        \PY{k}{except} \PY{n+ne}{AttributeError}\PY{p}{:}
            \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{cls}\PY{o}{.}\PY{n}{find\PYZus{}method}\PY{p}{(}\PY{n}{name}\PY{p}{)}
\end{Verbatim}

>>>>

\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{class} \PY{n+nc}{VersionTag}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{pass}

\PY{k}{class} \PY{n+nc}{Class}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}
    \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{n}{name}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{version} \PY{o}{=} \PY{n}{VersionTag}\PY{p}{(}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{find\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self} \PY{o}{=} \PY{n}{hint}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{promote}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
        \PY{n}{version} \PY{o}{=} \PY{n}{hint}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{version}\PY{p}{,} \PY{n}{promote}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
        \PY{n}{result} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{\PYZus{}find\PYZus{}method}\PY{p}{(}\PY{n}{name}\PY{p}{,} \PY{n}{version}\PY{p}{)}
        \PY{k}{if} \PY{n}{result} \PY{o+ow}{is} \PY{o+ow}{not} \PY{n+nb+bp}{None}\PY{p}{:}
            \PY{k}{return} \PY{n}{result}
        \PY{k}{raise} \PY{n+ne}{AttributeError}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{n+nd}{@purefunction}
    \PY{k}{def} \PY{n+nf}{\PYZus{}find\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{version}\PY{p}{)}\PY{p}{:}
        \PY{k}{return} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{o}{.}\PY{n}{get}\PY{p}{(}\PY{n}{name}\PY{p}{)}

    \PY{k}{def} \PY{n+nf}{change\PYZus{}method}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{value}\PY{p}{)}\PY{p}{:}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{methods}\PY{p}{[}\PY{n}{name}\PY{p}{]} \PY{o}{=} \PY{n}{value}
        \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{version} \PY{o}{=} \PY{n}{VersionTag}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
